Ecuador plant species GBIF

### 2023-01-23 code/L0/L0_Ecuador_plants_GBIF.Rmd
knit to html

```{r}
# using summarytools package
d_summary <- dfSummary(d, 
            na.col       = FALSE,
            style        = "multiline",
            plain.ascii  = TRUE,
            graph.magnif = .8)
print(d_summary, method = "render")
view(d_summary, file = file.path(output_path,"Ecuador_BIEN_traits_summary.html"))
```

```{r}
#using bdvis package
d <- format_bdvis(d, , Latitude = "decimalLatitude", Longitude = "decimalLongitude", Date_collected = "eventDate", Scientific_name = "scientificName", Family = "family", Genus = "genus")
```

```{r}
bdsummary(d)
d$Date_collected <- as.Date(d$Date_collected)
bdcalendarheat(d)
getcellid(d, gridscale = 10)
distrigraph(d, ptype = "species")
distrigraph(d, ptype = "efforts")
distrigraph(d, ptype = "cell")
distrigraph(d, ptype = "effortspecies")
bdcomplete(d)
mapgrid(d, ptype = "species", region = "Ecuador")
```

>>>>

```{r}
# using summarytools package
# ERROR -- Error in hist.default(data, breaks = breaks_x, plot = FALSE) :
# some 'x' not counted; maybe 'breaks' do not span range of 'x'
#d_summary <- dfSummary(d, 
#            na.col       = FALSE,
#            style        = "multiline",
#            plain.ascii  = TRUE,
#            graph.magnif = .8)
#print(d_summary, method = "render")
#view(d_summary, file = file.path(output_path,"Ecuador_BIEN_traits_summary.html"))
```

```{r}
#using bdvis package
d <- format_bdvis(d, Latitude = "decimalLatitude", Longitude = "decimalLongitude", Date_collected = "eventDate", Scientific_name = "scientificName", Family = "family", Genus = "genus")
bdsummary(d)
```

```{r}
## ERROR - Error in !dbPreExists : invalid argument type
## ERROR - Error in postgresqlNewConnection(drv, ...) :
# RPosgreSQL error: could not connect postgres@localhost:5432 on dbname "test": could not connect to server: Connection refused (0x0000274D/10061)
#bdcalendarheat(d)
#distrigraph(d, ptype = "species")
#distrigraph(d, ptype = "efforts")
#distrigraph(d, ptype = "cell")
#distrigraph(d, ptype = "effortspecies")
#bdcomplete(d)
#mapgrid(d, ptype = "species", region = "Ecuador")
```
